### 2018-02-10 Writing/Thesis/content/chapter-evaluation.tex
added timings and removed todopackage

\subsection{Time}
\hspace{-1em}
\begin{table}[h]
	\begin{tabularx}{1.1\textwidth}{>{\hsize=2.6\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X| >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X}
		Ranker 				& \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Ranker Build Time (ms)} & \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Ranker Prediction Time (ms)} \\ \cline{2-9}
										& Min		& Max		& Mean		& Stdv 	& Min	& Max		& Mean		& Stdv 	\\ \hline
		LinearRegression 				& 1454 		& 2060 		& 1580	 	& 36 	& 0 		& 86.667 	& 3.469	 	& 7.244 	\\
		M5P				 				& 3145 		& 4916 		& 3226	 	& 89 	& 0 		& 82.353 	& 3.78	 	& 6.535	\\	
		RandomForest		 				& 6048 		& 9720 		& 6236	 	& 259 	& 0		& 60 		& 3.097 		& 5.745	\\	
		REPTree			 				& 599 		& 1264 		& 629		& 38 	& 0 		& 82.353		& 4.829	 	& 7.948	\\	
		InstanceBased 					& 66 		& 550 		& 90	 		& 25 	& 0 		& 82.353		& 5.401 		& 9.44	\\	
		InstanceBased\footnotemark{}		& 66 		& 138 		& 88	 		& 12 	& 0 		& 98.367 	& 5.437 		& 10.323	\\	
		InstanceBased\footnotemark{}		& 66 		& 163		& 87	 		& 12 	& 0 		& 82.353 	& 5.382	 	& 9.402	\\	
		PairwiseComparison 				& 11784 		& 15096		& 12623	 	& 348 	& 0 		& 97.822 	& 9.762	 	& 13.135	\\	
		BestAlgorithm	 				& 193	 	& 321		& 221	 	& 23	 	& 0		& 82.353		& 6.480 		& 10.168	\\							
	\end{tabularx}
	\label{tab:evaluationresults1}
	\caption{Build and Prediction Times of the Rankers in ms (full meta data)}
\end{table}

>>>>

\subsection{Time}
\hspace{-1em}
\begin{table}[h]
	\begin{tabularx}{1.1\textwidth}{>{\hsize=2.6\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X| >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X}
		Ranker 				& \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Ranker Build Time (ms)} & \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Ranker Prediction Time (ms)} \\ \cline{2-9}
										& Min		& Max		& Mean		& Stdv 	& Min	& Max		& Mean		& Stdv 	\\ \hline
		LinearRegression 				& 1454 		& 2060 		& 1580	 	& 36 	& 0 		& 1      	& 0	 	    & 0 	\\
		M5P				 				& 3145 		& 4916 		& 3226	 	& 89 	& 0 		& 16		 	& 0	 		& 1	\\	
		RandomForest		 				& 6048 		& 9720 		& 6236	 	& 259 	& 0		& 16 		& 3	 		& 2	\\	
		REPTree			 				& 599 		& 1264 		& 629		& 38 	& 0 		& 16			& 1	 		& 16	\\	
		InstanceBased 					& 66 		& 550 		& 90	 		& 25 	& 0 		& 47			& 5 			& 8	\\	
		InstanceBased\footnotemark{}		& 66 		& 138 		& 88	 		& 12 	& 0 		& 19		 	& 1			& 3	\\	
		InstanceBased\footnotemark{}		& 66 		& 163		& 87	 		& 12 	& 0 		& 16		 	& 1		 	& 2	\\	
		PairwiseComparison 				& 11784 		& 15096		& 12623	 	& 348 	& 0 		& 0 			& 9.762	 	& 13.135	\\	
		BestAlgorithm	 				& 193	 	& 321		& 221	 	& 23	 	& 0		& 0			&  0 		& 0\\							
	\end{tabularx}
	\label{tab:evaluationresults1}
	\caption{Build and Prediction Times of the Rankers in ms (full meta data)}
\end{table}

%TODO add values for pairwise comparision}
\addtocounter{footnote}{-2}
\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young}
\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young, Baselearner KNN with n=$\sqrt{\text{number of instances}}$}
